A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-02-14 main.tex
Thus, the biomarker discovery strategy is survival modeling through collections of $X_1...X_n$ features from cancer datasets.

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{
The survival analysis using the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC). It is necessary to determine a cutoff point by patients' dichotomization for the continuous gene expression. There is some optimization software for cutoff determination. However, that software's predetermined cutoffs have been set at the median or quantiles of RNA sequencing value to perform the survival analysis. 
%There are few clinicopathological features available on those pre-processed datasets. (feature selection or feature engineering issue)
We developed a comprehensive workflow to perform biomarker discovery. It includes data retrieval, data pre-processing, feature selection, cutoff engine, Kaplan-Meier survival analysis, and Cox proportional hazard modeling.
Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes and adjusted them with confounders and Bonferroni corrected P-value.
The result showed that ten over-expressed genes (named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) 
are significantly associated with a poor prognosis of overall survival. 
Furthermore, the other ten over-expressed genes (named ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former name as KIAA1683, and NPB) are correlated with better survival.
We suggest this workflow could help for biomarker discovery.
}

@@

\begin{figure}
    \centering
    \includegraphics[width=14cm]{graphic_abstract_pvalueTex.pdf}
    \caption{(inset image courtesy of National Cancer Institute\cite{nci1950})}
    \label{fig:my_label}
\end{figure}

@@

Head and neck squamous cell carcinoma (\acrshort{hnscc}), including oral, oropharyngeal, and hypopharyngeal origin, is the fourth leading cancer causes of death for males in Taiwan\cite{MOHW_death2017}. The age-standardized incidence rate of \acrshort{hnscc} in males is 42.43 per 100,000 persons\cite{MOHW_incidence2018}. 
% chemotherapy => systemic therapy
The treatment strategies of \acrshort{hnscc} are surgery alone, systemic therapy with concurrent radiation therapy (systemic therapy/\acrshort{rt}), or surgery with adjuvant systemic therapy/\acrshort{rt} (according to \acrlong{nccn}, \acrshort{nccn} Clinical Practice Guidelines in \acrshort{hnscc}, Version 2.2020)\cite{Pfister2020a}. Despite the improvement in those interventions, the survival of \acrshort{hnscc} has improved only marginally over the past decade worldwide\cite{hpa2019}. The critical advancement of targeted therapy and immuno-oncology should benefit from emerging prognostic biomarkers, which guide the development of modern systemic therapy.

@@

%\begin{MyColorPar}{red}
%%%%%% revision1 added [TCGA] [2021/02/02]
The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005.
TCGA represents comprehensive genomics and clinic data from 84,392 patients among 33 major cancer types (data release 27.0 - Oct 29, 2020, available at https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/studied-cancers).
%The Cancer Genome Atlas (TCGA): The TCGA consortium, which is a National Institute of Health (NIH) initiative, makes publicly available molecular and clinical information for more than 33 types of human cancers including exome (variant analysis), single nucleotide polymorphism (SNP), DNA methylation, transcriptome (mRNA), microRNA (miRNA) and proteome.
TCGA and other collaborated \acrfull{gdac} generated and analyzed DNA (mutation, copy number variation, methylation, simple nucleotide polymorphism, SNP), RNA (microarray, RNA-Seq, microRNA), and protein (reverse protein phased array) data derived from biospecimen. Sample types available at TCGA are primary solid tumors, recurrent solid tumors, blood-derived normal and tumor, metastatic, and solid tissue normal.

@@

% to summarize the advantages of its use.
The highlights of the advantages of applying the TCGA data for cancer research include:
\begin{outline}
\1  To the best of our knowledge, the TCGA database is the largest collection (cancer types and cohort size) of comprehensive genomics with survival data available in the field of cancer research so far. The whole-genome sequencing data has been harmonized across all GDACs. The basic demographic data is usually available on many databases. However, TCGA data has more comprehensive features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
\1  TCGA has a remarkable advantage for computational and life scientists who study cancer since useful web-tools and API are ready to analyze and visualize TCGA data. It might be getting help quickly from the research community for trouble-shooting.
\1  Many achievements of diagnoses, treatments, and prevention with the TCGA data have already been published and keep growing.\cite{Tomczak2015}
\end{outline}

@@

%\subsubsection{Figure 1:h}
\begin{figure}[hp]
\centering
\includegraphics[width=14cm]{Figure_1_manuscript_workflow} % .PDF is better than .png
%, height=8cm
%\caption
\bcaption{A workflow of \acrshort{hnscc} biomarker discovery, step 1 (blue line: main procedure) and step 2 (orange line: analysis export).}
%Step 3 (purple line: dealing with surgical margin).
{The "main procedure" includes data retrieving from TCGA GDC data portal, data process with merging and cleaning, then performing the survival analyses. The Cutoff engine (cutofFinder\_func.HNSCC.R) might calculate all possible Kaplan-Meier P-value to find the optimal cutoff value of RNA-Seq for subsequent Cox modeling (a draft diagram shown on the upper right corner "HNSCC cohort", the serial cut for grouping patients with low [green] or high [red] expression of a specific gene, to yield a collection of P-values; please see Materials and Methods section for details). The step 2 "analysis export" performs dissecting and selection of candidate genes by Bonferroni adjusted P-value as well as a hazard ratio of Cox model, which was based on the results from the step 1.
(HNSCC: head and neck squamous cell carcinoma; TCGA: the Cancer Genome Atlas; RNA-Seq: RNA sequencing; GDC: Genomic Data Commons.)}
\label{fig:figure1}
\end{figure}

@@

The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated at workflow step 1 (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
By uncorrected P-value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b)  multivariate plots). At the final step, a Bonferroni P-value correction was used to yield the twenty candidate genes, under the stringent criteria (see Figure \ref{fig:figure2}(c), (d)). The ten candidates, including DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, have significantly associated with the poor prognosis of \acrshort{os} (see Table \ref{table:table1}),
%\subsubsection{Figure 3}
while the other ten genes were over-expressed in the better survival patients, named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB (see Table \ref{table:table3}, with their full name of genes).
We made a volcano plot for 9416 genes by Kaplan-Meier P-value (less than 0.05, obtained during cutoff finding procedure) against the Cox hazard ratio (see Figure \ref{fig:figure3}). The plot revealed that the most significant (Bonferroni-adjusted P-value $< 0.05$) candidate genes are located above the dotted line. At the same time, Cox's HR separated them on the two-side with prognostic impact.

%\subsubsection{Figure 2:h}
\begin{figure}[hp]
\centering
\includegraphics[width=14cm]{Figure2.pdf}
\bcaption{\acrshort{hnscc} Cox's hazard ratio and P-value plots.}
{(a) Univariate HR versus uncorrected P-value; (b) Multivariate HR versus uncorrected P-value; (c) Univariate HR versus Bonferroni corrected P-value; and (d) Multivariate HR versus Bonferroni corrected P-value.}
\label{fig:figure2}
\end{figure}

@@

\caption{ The 10 candidate genes over-expressed with poor prognosis in \acrshort{hnscc} (ranked by Bonferroni adjusted P-value) }

@@

\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{P-value}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Adjusted \\P-value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI                                    &                                             \\ 

@@

\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni adjusted P-value $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\ 

@@

\multicolumn{9}{|l!{\color{black}\vrule}}{* Cox's model: P-value $< 0.001$ }                                                                                                                                                                                                                                                                                                                                                                                                  \\ 

@@

\caption{The 10 candidate genes over-expressed with better prognosis in \acrshort{hnscc} (ranked by Bonferroni corrected P-value) }

@@

\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Adjusted\\~P-value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{l|}{}                         \\ 

@@

\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni adjusted P-value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\* Cox's model: P-value \textless{} 0.001\\Remark: number off articles related to cancer research; ** as many~\\lncRNA: Long non-coding RNA\end{tabular}}                                                                                                                                                                                                                 \\

@@

%\subsubsection{Figure 3:h}
\begin{figure}[hp]
\centering
\includegraphics[width=14cm]{TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR-Figure3.pdf} % .png from PvalueplotKM_20genes_Bonf.pdf
\bcaption{Volcano plot of genes under survival analyses.}
{X axis: unadjusted P-value of Kaplan-Meier survival (-log10 transformed).
Y axis: multivariate hazard ratio from Cox proportional regression model.
Dotted line: significant Bonferroni corrected P-value. 
Red circles mark 10 candidate genes, which impact on poor prognosis ($HR>=1.5$). Green circles mark 10 genes, which affect on better survival ($HR<=0.5$).}
\label{fig:figure3}
\end{figure}
% new figure of volcano plot: TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR.pdf, -log10(raw KM P-value) vs Cox multivariate HR
% X axis: "frequency" (number of uncorrected P-values less than 0.05 during Kaplan-Meier cutoff finding procedure). X axis: adjusted Kaplan-Meier P-value.

@@

Our top 1 candidate is \acrfull{DKK1} (see Figure \ref{fig:figure4}(a)). The Kaplan-Meier curve revealed 227 patients bearing the higher expression of \acrshort{DKK1} were suffered from only 40\% of 5-year \acrshort{os} rate. In comparison, the other 187 patients with lower expression (the cutoff at -0.312(RSEM)) have been a better prognosis (adjusted P-value as $0.001$).
Figure \ref{fig:figure4}(b)'s cumulative P-value plot showed that the uncorrected 116 P-values ($< 0.05$) were estimated by a serial cut from 125 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, "HNSCC cohort"). The smallest P-value (\num{8.9e-8}), when cut on n=187 (45.2\% of 414), was defined as optimal P-value.
Conversely, the most associated gene with better survival is \acrfull{ZNF557}. In Figure \ref{fig:figure4}(c), a Kaplan-Meier curve revealed 264 patients bearing the higher expression of \acrshort{ZNF557} have 55\% of 5-year OS survival rate (adjusted P-value = $0.001$). The cutoff finding procedure (cutofFinder\_func.R) generated cumulative P-value plots in Figure \ref{fig:figure4}(d). There were 166 uncorrected P-values estimated by a serial cut from 125 to 290 for grouping the cohort. All was less than 0.05, and the smallest P-value (\num{8.6e-8}), when cut on n=150 (36.2\% of total cohort 414), was defined as optimal P-value with a cutoff value -0.511(RSEM) of \acrshort{rnaseq}.
%The second candidate, which improving patient survival, is ZNF266.
%\subsubsection{Tables} in main article

%\subsubsection{Figure 4:h}
\begin{figure}[hp]
\centering
\includegraphics[width=15cm]{Figure4.pdf}
\bcaption{Kaplan-Meier survival analyses, by cutoff finding.}
{(a) Kaplan-Meier plot of DKK1 under optimal P-value, and (b) the cutoff was derived from cumulative P-value plots of DKK1. (c) Kaplan-Meier plot of ZNF557 under optimal P-value, and (d) the cutoff was derived from cumulative P-value plots of ZNF557.}
\label{fig:figure4}
\end{figure}

@@

Table \ref{table:table1} showed ten candidate genes over-expressed with poor prognosis in \acrshort{hnscc}, ranked by adjusted Kaplan-Meier P-value. We found their Cox's univariate and multivariate HR are all greater than 1.837. There were few published articles of \acrfull{SURF4} and \acrfull{NDFIP1} (\acrshort{NEDD4}: \acrlong{NEDD4}), which were related to cancer research.
In Table \ref{table:table2},
after adjustment of confounders, it was considered the \acrshort{DKK1} over-expression is the independent prognostic factor (multivariate HR 2.135 [95\% CI: 1.559-2.924, P-value $<$ 0.001]), as well as clinical T stage (HR 1.978 [95\% CI: 1.046-3.737, P-value = 0.036]) and surgical margins status (HR 1.601 [95\% CI: 1.159-2.211, P-value = 0.004]). The age older than 65 year-old has negative influence on survival (HR 1.462 [95\% CI: 1.078-1.983, P-value = 0.015]). The M stage could not be considered due to only 3 out of 414 patients which have distant metastasis.

@@

\multicolumn{2}{|c!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                             & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{P-value}                              \\ 

@@

\multicolumn{8}{|l|}{(P-value significant codes is denoted: $red<0.05$; *** $<0.001$~~)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\

@@

There were also ten candidate genes over-expressed with a better prognosis of \acrshort{hnscc}, listed in Table \ref{table:table3}. Cox's univariate and multivariate HR is just under 0.5.
In Table \ref{table:table4},
after adjustment of confounders, it revealed HR 1.961 [95\% CI: 1.035-3.714, P-value = 0.039] in advance clinical T Status, HR 1.631 [95\% CI: 1.18-2.254, P-value = 0.003] with positive surgical margin involvement, HR 1.453 [95\% CI: 1.055-2.000, P-value = 0.022] with higher tobacco exposure, and a protective HR 0.499 [95\% CI: 0.372-0.669, P-value $<$ 0.001] in over-expressed \acrshort{ZNF557} gene.

@@

\subsection{holistic}
TCGA 都是手術後？TNM available yes
discussion: limitation
the TCGA has not collected holistic features
癌症與身心靈的重要關係：中醫、citation?
repentantly confess for not taking care of body and spirit, and sincere thanks for the hard work of my physical body
自他不二
心存正念
1.衷心懺悔
2.真心感謝
3.誠意祝福
4.永存善念
5.心無恐懼: 情志養生

祝福全世界

>>>>

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{
Survival analysis using the Cancer Genome Atlas (TCGA) dataset is a well-known method to discover gene expression-based prognostic biomarkers of head and neck squamous cell carcinoma (HNSCC). It is necessary to determine a cutoff point by patients' dichotomization for the continuous gene expression. Usually, an optimization algorithm for cutoff determination has been set at the median or quantiles of RNA sequencing value.
%There are few clinicopathological features available on those pre-processed datasets. (feature selection or feature engineering issue)
We developed a comprehensive workflow to perform biomarker discovery. It includes data retrieval, data pre-processing, feature selection, cutoff engine, Kaplan-Meier survival analysis, and Cox proportional hazard modeling.
Using this workflow on the TCGA HNSCC cohort, we scanned human protein-coding genes and adjusted them with confounders and Bonferroni corrected \textit{P} value.
The result showed that ten over-expressed genes (named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1) 
are significantly associated with a poor prognosis of overall survival. 
Furthermore, the other ten over-expressed genes (named ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN - former name as KIAA1683, and NPB) are correlated with better survival.
We suggest this workflow equipped with a cutoff-mining engine could help for biomarker discovery.
}

@@

%\begin{figure}
%    \centering
%    \includegraphics[width=14cm]{graphic_abstract_pvalueTex.pdf}
%    \caption{(inset image courtesy of National Cancer Institute\cite{nci1950})}
%    \label{fig:my_label}
%\end{figure}

@@

Head and neck squamous cell carcinoma (\acrshort{hnscc}), including oral, oropharyngeal, and hypopharyngeal origin, is the fourth leading cancer causes of death for males in Taiwan\cite{MOHW_death2017}. The age-standardized incidence rate of \acrshort{hnscc} in males is 42.43 per 100,000 persons\cite{MOHW_incidence2018}. 
% chemotherapy => systemic therapy
The treatment strategies of \acrshort{hnscc} are surgery alone, systemic therapy with concurrent radiation therapy (systemic therapy/\acrshort{rt}), or surgery with adjuvant systemic therapy/\acrshort{rt} (according to \acrlong{nccn}, \acrshort{nccn} Clinical Practice Guidelines in \acrshort{hnscc}, Version 2.2020)\cite{Pfister2020a}. Despite the improvement in those interventions, the survival of \acrshort{hnscc} has improved only marginally over the past decade worldwide\cite{hpa2019}. The critical advancement of targeted therapy and immuno-oncology should benefit from emerging prognostic  biomarkers guiding modern systemic therapy.

%latex https://www.latex-tutorial.com/symbols/greek-alphabet/
\subsection*{Linear regression in biomarker discovery}
Linear regression is useful as a concept in biomarker discovery.
A linear regression equation that relates a Y-variable to n X-variables is written as%\\[1cm]
\par
%Highlights
% https://quicklatex.com
\begin{flushleft}
% equation
%\begin{math}

ground truth Y (e.x. patient's survival):\\[0.5cm]
%Y$:\\[0.3cm]
$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$
\linebreak
\linebreak
Input $X_1...n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)
\\[0.5cm]
Coefficients $\beta_0...n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)\\[0.5cm]
A residual (error) term is calculated as $\epsilon=Y - \hat Y$\\
Since the model established by survival analysis, predicted value $\hat Y$ is calculated as:\\[0.3cm]
$\hat Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n$
\linebreak
%(predicted Y, output) intercept, slope, independent (input) \Times
%\end{math}
\end{flushleft}
Thus, the biomarker discovery strategy is survival modeling through collections of $X_1...X_n$ features from cancer datasets.

@@

\subsection{A introduction of TCGA}
%\begin{MyColorPar}{red}
%%%%%% revision1 added [TCGA] [2021/02/02]
The Cancer Genome Atlas (TCGA) project\cite{Weinstein2013} is developed and supervised by the National Cancer Institute's (NCI) Center for Cancer Genomics and the National Human Genome Research Institute (NHGRI), funded by the US government since 2005.
TCGA represents comprehensive genomics and clinic data from 84,392 patients among 33 major cancer types (data release 27.0 - Oct 29, 2020, available at https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/studied-cancers).
%The Cancer Genome Atlas (TCGA): The TCGA consortium, which is a National Institute of Health (NIH) initiative, makes publicly available molecular and clinical information for more than 33 types of human cancers including exome (variant analysis), single nucleotide polymorphism (SNP), DNA methylation, transcriptome (mRNA), microRNA (miRNA) and proteome.
TCGA and other collaborated \acrfull{gdac} generated and analyzed DNA (mutation, copy number variation, methylation, simple nucleotide polymorphism, SNP), RNA (microarray, RNA-Seq, microRNA), and protein (reverse protein phased array) data derived from biospecimen. Sample types available at TCGA are primary solid tumors, recurrent solid tumors, blood-derived normal and tumor, metastatic, and solid tissue normal.

@@

% to summarize the advantages of its use.
The highlights of the advantages of applying the TCGA data for cancer research include:
\begin{outline}
\1  To the best of our knowledge, the TCGA database is the largest collection (cancer types and cohort size) of comprehensive genomics with survival data available in the field of cancer research so far. 
There are many $X_1 ... X_n$ physical and social features of patients available for survival modelling.
The whole-genome sequencing data has been harmonized across all GDACs. The basic demographic data is usually available on many databases. However, TCGA data has more comprehensive features, such as exposure to alcohol, asbestos, radioactive radon, tobacco smoking, or cigarettes.
\1  TCGA has a remarkable advantage for computational and life scientists who study cancer since useful web-tools and API are ready to analyze and visualize TCGA data. It might be getting help quickly from the research community for trouble-shooting.
\1  Many achievements of diagnoses, treatments, and prevention with the TCGA data have already been published and keep growing.\cite{Tomczak2015}
\end{outline}

@@

%\subsubsection{Figure 1:h}
\begin{figure}[hp]
\centering
\includegraphics[width=14cm]{Figure_1_manuscript_workflow} % .PDF is better than .png
%, height=8cm
%\caption
\bcaption{A workflow of \acrshort{hnscc} biomarker discovery, step 1 (blue line: main procedure) and step 2 (orange line: analysis export).}
%Step 3 (purple line: dealing with surgical margin).
{The "main procedure" includes data retrieving from TCGA GDC data portal, data process with merging and cleaning, then performing the survival analyses. The Cutoff engine (cutofFinder\_func.HNSCC.R) might calculate all possible Kaplan-Meier \textit{P} value to find the optimal cutoff value of RNA-Seq for subsequent Cox modeling (a draft diagram shown on the upper right corner "HNSCC cohort", the serial cut for grouping patients with low [green] or high [red] expression of a specific gene, to yield a collection of \textit{P} values; please see Materials and Methods section for details). The step 2 "analysis export" performs dissecting and selection of candidate genes by Bonferroni adjusted \textit{P} value as well as a hazard ratio of Cox model, which was based on the results from the step 1.
(HNSCC: head and neck squamous cell carcinoma; TCGA: the Cancer Genome Atlas; RNA-Seq: RNA sequencing; GDC: Genomic Data Commons.)}
\label{fig:figure1}
\end{figure}

@@

The 9416 Kaplan-Meier plots with associated Cox's univariate and multivariate tables were generated at workflow step 1 (see Figure \ref{fig:figure1}) and justified by the ranking of hazard ratios.
By uncorrected \textit{P} value below 0.05, we selected 967 genes in which \acrfull{hr} is greater than 1.5 or less than 0.5 (see Figure \ref{fig:figure2}(a) univariate, and Figure \ref{fig:figure2}(b)  multivariate plots). At the final step, a Bonferroni \textit{P} value correction was used to yield the twenty candidate genes, under the stringent criteria (see Figure \ref{fig:figure2}(c), (d)). The ten candidates, including DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, have significantly associated with the poor prognosis of \acrshort{os} (see Table \ref{table:table1}),
%\subsubsection{Figure 3}
while the other ten genes were over-expressed in the better survival patients, named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB (see Table \ref{table:table3}, with their full name of genes).
We made a volcano plot for 9416 genes by Kaplan-Meier \textit{P} value (less than 0.05, obtained during cutoff finding procedure) against the Cox hazard ratio (see Figure \ref{fig:figure3}). The plot revealed that the most significant (Bonferroni-adjusted \textit{P} $< 0.05$) candidate genes are located above the dotted line. At the same time, Cox's HR separated them on the two-side with prognostic impact.

%\subsubsection{Figure 2:h}
\begin{figure}[hp]
\centering
\includegraphics[width=14cm]{Figure2.pdf}
\bcaption{\acrshort{hnscc} Cox's hazard ratio and \textit{P} value plot.}
{(a) Univariate HR versus uncorrected \textit{P} value; (b) Multivariate HR versus uncorrected \textit{P} value; (c) Univariate HR versus Bonferroni corrected \textit{P} value; and (d) Multivariate HR versus Bonferroni corrected \textit{P} value.}
\label{fig:figure2}
\end{figure}

@@

\caption{ The 10 candidate genes over-expressed with poor prognosis in \acrshort{hnscc} (ranked by Bonferroni adjusted \textit{P} value) }

@@

\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{\textit{P} value}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Adjusted \\\textit{P} value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI                                    &                                             \\ 

@@

\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\ 

@@

\multicolumn{9}{|l!{\color{black}\vrule}}{* Cox's model: \textit{P} $< 0.001$ }                                                                                                                                                                                                                                                                                                                                                                                                  \\ 

@@

\caption{The 10 candidate genes over-expressed with better prognosis in \acrshort{hnscc} (ranked by Bonferroni corrected \textit{P} value) }

@@

\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\textit{P} value}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Adjusted\\~\textit{P} value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{l|}{}                         \\ 

@@

\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\* Cox's model: \textit{P} value \textless{} 0.001\\Remark: number off articles related to cancer research; ** as many~\\lncRNA: Long non-coding RNA\end{tabular}}                                                                                                                                                                                                                 \\

@@

%\subsubsection{Figure 3:h}
\begin{figure}[hp]
\centering
\includegraphics[width=14cm]{TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR-Figure3.pdf} % .png from PvalueplotKM_20genes_Bonf.pdf
\bcaption{Volcano plot of genes under survival analyses.}
{X axis: unadjusted \textit{P} value of Kaplan-Meier survival (-log10 transformed).
Y axis: multivariate hazard ratio from Cox proportional regression model.
Dotted line: significant Bonferroni corrected \textit{P} value. 
Red circles mark 10 candidate genes, which impact on poor prognosis ($HR>=1.5$). Green circles mark 10 genes, which affect on better survival ($HR<=0.5$).}
\label{fig:figure3}
\end{figure}
% new figure of volcano plot: TCGA_HNSC_Optimal_Overall_allPlot_unKM_P_multiHR.pdf, -log10(raw KM P-value) vs Cox multivariate HR
% X axis: "frequency" (number of uncorrected P-values less than 0.05 during Kaplan-Meier cutoff finding procedure). X axis: adjusted Kaplan-Meier P-value.

@@

Our top 1 candidate is \acrfull{DKK1} (see Figure \ref{fig:figure4}(a)). The Kaplan-Meier curve revealed 227 patients bearing the higher expression of \acrshort{DKK1} were suffered from only 40\% of 5-year \acrshort{os} rate. In comparison, the other 187 patients with lower expression (the cutoff at -0.312(RSEM)) have been a better prognosis (adjusted \textit{P} = $0.001$).
Figure \ref{fig:figure4}(b)'s cumulative \textit{P} value plot showed that the uncorrected 116 \textit{P} values ($< 0.05$) were estimated by a serial cut from 125 to 290 persons for grouping the cohort in our cutoff finding procedure (cutofFinder\_func.R, see Figure \ref{fig:figure1}, "HNSCC cohort"). The smallest \textit{P} value (\num{8.9e-8}), when cut on n=187 (45.2\% of 414), was defined as optimal \textit{P} value.
Conversely, the most associated gene with better survival is \acrfull{ZNF557}. In Figure \ref{fig:figure4}(c), a Kaplan-Meier curve revealed 264 patients bearing the higher expression of \acrshort{ZNF557} have 55\% of 5-year OS survival rate (adjusted \textit{P} = $0.001$). The cutoff finding procedure (cutofFinder\_func.R) generated cumulative \textit{P} value plots in Figure \ref{fig:figure4}(d). There were 166 uncorrected \textit{P} values estimated by a serial cut from 125 to 290 for grouping the cohort. All was less than 0.05, and the smallest \textit{P} value (\num{8.6e-8}), when cut on n=150 (36.2\% of total cohort 414), was defined as optimal \textit{P} value with a cutoff value -0.511(RSEM) of \acrshort{rnaseq}.
%The second candidate, which improving patient survival, is ZNF266.
%\subsubsection{Tables} in main article

%\subsubsection{Figure 4:h}
\begin{figure}[hp]
\centering
\includegraphics[width=15cm]{Figure4.pdf}
\bcaption{Kaplan-Meier survival analyses, by cutoff finding.}
{(a) Kaplan-Meier plot of DKK1 under optimal \textit{P} value, and (b) the cutoff was derived from cumulative \textit{P} value plot of DKK1. (c) Kaplan-Meier plot of ZNF557 under optimal \textit{P} value, and (d) the cutoff was derived from cumulative \textit{P} value plot of ZNF557.}
\label{fig:figure4}
\end{figure}

@@

Table \ref{table:table1} showed ten candidate genes over-expressed with poor prognosis in \acrshort{hnscc}, ranked by adjusted Kaplan-Meier \textit{P} value. We found their Cox's univariate and multivariate HR are all greater than 1.837. There were few published articles of \acrfull{SURF4} and \acrfull{NDFIP1} (\acrshort{NEDD4}: \acrlong{NEDD4}), which were related to cancer research.
In Table \ref{table:table2},
after adjustment of confounders, it was considered the \acrshort{DKK1} over-expression is the independent prognostic factor (multivariate HR 2.135 [95\% CI: 1.559-2.924, \textit{P} $<$ 0.001]), as well as clinical T stage (HR 1.978 [95\% CI: 1.046-3.737, \textit{P} = 0.036]) and surgical margins status (HR 1.601 [95\% CI: 1.159-2.211, \textit{P} = 0.004]). The age older than 65 year-old has negative influence on survival (HR 1.462 [95\% CI: 1.078-1.983, \textit{P} = 0.015]). The M stage could not be considered due to only 3 out of 414 patients which have distant metastasis.

@@

\multicolumn{2}{|c!{\color{black}\vrule}}{}                                                                                   & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{\textit{P} value}                             & \multicolumn{1}{c!{\color{black}\vrule}}{HR}                                   & \multicolumn{1}{c!{\color{black}\vrule}}{CI95\%}                              & \multicolumn{1}{c!{\color{black}\vrule}}{\textit{P} value}                              \\ 

@@

\multicolumn{8}{|l|}{(\textit{P} value significant codes is denoted: $red<0.05$; *** $<0.001$~~)}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           \\

@@

There were also ten candidate genes over-expressed with a better prognosis of \acrshort{hnscc}, listed in Table \ref{table:table3}. Cox's univariate and multivariate HR is just under 0.5.
In Table \ref{table:table4},
after adjustment of confounders, it revealed HR 1.961 [95\% CI: 1.035-3.714, \textit{P} = 0.039] in advance clinical T Status, HR 1.631 [95\% CI: 1.18-2.254, \textit{P} = 0.003] with positive surgical margin involvement, HR 1.453 [95\% CI: 1.055-2.000, \textit{P} = 0.022] with higher tobacco exposure, and a protective HR 0.499 [95\% CI: 0.372-0.669, \textit{P} $<$ 0.001] in over-expressed \acrshort{ZNF557} gene.

@@

\subsection{Holistic health care}
TCGA treated by surgery and more; TNM available yes
discussion: limitation
Even there are many $X_1 ... X_n$ physical and social features of patients available for survival modelling in the TCGA.
the TCGA has not collected holistic features
%癌症與身心靈的重要關係：中醫、citation? 中醫人體觀－五臟與經絡情緒 工作坊《課程簡介》情緒是人體自身的氣，我們因情緒而調動它，也因它內傷，誘發情緒的原因有外在和內在，外在多跟經絡接收訊息的能力有關，當外在的影響如果沒有適當阻斷的時候，也會影響到五臟功能；內生的情緒則多以活出自我價值感有關，當我們活出此生想要體驗的人生與成就，我們就能夠不受情緒控制而保持內在平靜，這一切的源頭皆與我們是否活出真實的自己有關。
repentantly confess for not taking care of body and spirit, and sincere thanks for the hard work of my physical body
%自他不二 心存正念
%1.衷心懺悔
%2.真心感謝
%3.誠意祝福
%4.永存善念
%5.心無恐懼: 情志養生
